
\documentclass{beamer}
\usepackage{graphicx}
\usepackage{hyperref}

\title{Zombie Wars}
\subtitle{A Thrilling Battle for Survival}
\author{Team CodHers\\Annapurna Adhikari, Chitti Thalli Kaja, Kashika Malhotra, Khushleen Kaur, Vaishnavi Vikramsinh Bhosale}
\date{\today}

\begin{document}

\frame{\titlepage}

\begin{frame}
\frametitle{Introduction}
\begin{itemize}
  \item \textbf{Overview}: 
  \\\textit{Zombie Wars} is an action-packed game where players must survive waves of enemies and strategically use their resources to progress.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Game Features}
\begin{itemize}
  \item Player Movement: Smooth and intuitive controls for navigating the game world.
  \item Weapons: 5 unique weapons, each with different strengths.
  \item Healing Mechanic: Players can heal themselves using energy collected during gameplay.
  \item Enemy Variety: Diverse enemies with varying strengths to challenge the player.
  \item Player Customization: Control speed, magic power, attack power, and health using experience points (XP).
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Game Mechanics}
\begin{itemize}
  \item Movement: Arrow keys 
  \item Weapons: Switch between weapons using "q" key and attack using spacebar
  \item Magic: Press 'e' to switch between flame and heal. Press "ctrl" to use
\end{itemize}
\end{frame}


\begin{frame}
\frametitle{Development Tools}
\begin{itemize}
  \item Pygame: Used for game development and mechanics.
  \item Tiled: Utilized for creating and managing game maps.
  \item Version Control: Effective use of Git for collaboration and version management.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Teamwork and Coordination}
\begin{itemize}
  \item Collaboration: Seamless teamwork and communication within Team CodHers.
  \item Problem-Solving: Overcame challenges through collective brainstorming and cooperation.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Learnings and Achievements}
\begin{itemize}
  \item Technical Skills: Gained proficiency in Pygame and Tiled.
  \item Team Coordination: Enhanced ability to work as a cohesive unit.
  \item Version Control: Mastered the use of Git for efficient version management.
\end{itemize}
\end{frame}


\begin{frame}
  \frametitle{Resources}
  \begin{itemize}
    \item https://opengameart.org/
    \item https://www.flaticon.com/icons
    \item https://craftpix.net/categorys/sprites/ 
    \item https://www.pygame.org/docs/
  \end{itemize}
  \end{frame}


\begin{frame}
\frametitle{Demonstration}
\begin{itemize}
  \item Live Demo
\end{itemize}
\end{frame}



\begin{frame}
\frametitle{}
\center{Thank You!}
\end{frame}

\end{document}
